---
title: "Search Strategy Sensitivity Analysis"
subtitle: "Sexual Health in Neuromuscular Diseases - Scoping Review"
author: "Audrey El Kaïm"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(dplyr)
library(knitr)
library(kableExtra)
```

# Context

## Background

This scoping review aimed to map and synthesize evidence on sexual dysfunction in adults with neuromuscular diseases (NMDs). The original search strategy used umbrella terms ("neuromuscular disease", "neuromuscular disorder") combined with sexual health terms.

As PubMed MeSH does not include a single unified heading for all NMDs—distributing them across many disease-level MeSH terms—a sensitivity analysis was conducted to verify the comprehensiveness of the search strategy.

## Original Search Strategy

The original search strategy used umbrella terms:

```
("sexual behaviour"[MeSH Terms] OR "sexuality"[MeSH Terms] OR ...)
AND
("neuromuscular diseases"[MeSH Terms] OR "neuromuscular diseases"[All Fields]
 OR "neuromuscular disorders"[All Fields])
NOT (exclusions)
```

## Objective

To verify the comprehensiveness of the search strategy by:

1. Expanding the search with disease-specific and category terms
2. Comparing results with the original search
3. Identifying any additional relevant articles not captured by umbrella terms
4. Documenting all screening decisions for transparency

# Methods

## Extended Search Strategy

The search strategy was expanded to include:

### Disease Categories (Families)

- **Myopathies**: myopathy, muscular dystrophy, congenital myopathy, metabolic myopathy, mitochondrial myopathy
- **Inflammatory myopathies**: myositis, dermatomyositis, polymyositis, inclusion body myositis
- **Motor neuron diseases**: motor neuron disease, amyotrophic lateral sclerosis, spinal muscular atrophy, Kennedy disease (SBMA)
- **Peripheral neuropathies**: peripheral neuropathy, polyneuropathy, Charcot-Marie-Tooth disease, Guillain-Barré syndrome, CIDP
- **Neuromuscular junction disorders**: myasthenia gravis, Lambert-Eaton syndrome, congenital myasthenic syndromes
- **Channelopathies**: myotonic dystrophy, periodic paralysis, myotonia congenita
- **Specific dystrophies**: Duchenne, Becker, facioscapulohumeral, limb-girdle, Emery-Dreifuss
- **Metabolic myopathies**: Pompe disease, McArdle disease
- **Amyloid neuropathies**: transthyretin amyloidosis, familial amyloid polyneuropathy

### Important Methodological Note

**Ambiguous acronyms were avoided** to prevent false positives:

| Acronym | Intended meaning | Common false positive |
|---------|-----------------|----------------------|
| SMA | Spinal Muscular Atrophy | Smooth Muscle Actin |
| ALS | Amyotrophic Lateral Sclerosis | Various |
| BMD | Becker Muscular Dystrophy | Bone Mineral Density |
| MG | Myasthenia Gravis | Magnesium |
| FAP | Familial Amyloid Polyneuropathy | Familial Adenomatous Polyposis |
| IBM | Inclusion Body Myositis | Company name |

Only **full disease names** were used in the extended search.

## Search Execution

- **Database**: PubMed (via NCBI Entrez API)
- **Period**: 1983-2024 (matching the original review period)
- **Execution date**: `r format(Sys.time(), '%Y-%m-%d')`
- **Tool**: R scripts using the `rentrez` package

# Results

## Search Comparison

```{r load-data}
# Load results
original <- read.csv("results/pubmed_equation_originale.csv", stringsAsFactors = FALSE)
nouveaux_bruts <- read.csv("results/pubmed_NOUVEAUX_articles.csv", stringsAsFactors = FALSE)
haute_pertinence <- read.csv("results/pubmed_NOUVEAUX_HAUTE_PERTINENCE.csv", stringsAsFactors = FALSE)
final_table <- read.csv("results/FINAL_EXCLUSION_TABLE_EN.csv", stringsAsFactors = FALSE)
```

```{r summary-table}
summary_df <- data.frame(
  Step = c(
    "Original search (umbrella terms only)",
    "Extended search (disease-specific terms)",
    "New records (after deduplication)",
    "High relevance (NMD term in title)",
    "After removing duplicates with included studies",
    "Final: Articles meeting inclusion criteria"
  ),
  N = c(
    nrow(original),
    nrow(original) + nrow(nouveaux_bruts),
    nrow(nouveaux_bruts),
    nrow(haute_pertinence),
    nrow(final_table),
    sum(final_table$Decision == "INCLUDE")
  )
)

kable(summary_df, col.names = c("Step", "N articles"), align = c("l", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(6, bold = TRUE, background = "#d4edda")
```

## Screening Results

### Article Included

```{r included-article}
included <- final_table %>% filter(Decision == "INCLUDE")

if (nrow(included) > 0) {
  cat("**PMID:**", included$PMID[1], "\n\n")
  cat("**Year:**", included$Year[1], "\n\n")
  cat("**Title:**", included$Title[1], "\n\n")
  cat("**Content summary:**\n\n")
  cat(included$Justification[1])
}
```

### Articles Excluded (n = `r sum(final_table$Decision == "EXCLUDE")`)

```{r excluded-articles}
excluded <- final_table %>%
  filter(Decision == "EXCLUDE") %>%
  select(PMID, Year, Title, Justification)

kable(excluded, col.names = c("PMID", "Year", "Title", "Reason for exclusion")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE) %>%
  column_spec(3, width = "30%") %>%
  column_spec(4, width = "40%")
```

## Complete Screening Table (n = 16)

The following table presents all 16 articles identified through the extended search strategy, with screening decisions and detailed justifications.

```{r complete-table}
complete_table <- final_table %>%
  select(PMID, Year, Title, Decision, Justification)

kable(complete_table, col.names = c("PMID", "Year", "Title", "Decision", "Justification")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12) %>%
  column_spec(1, width = "8%") %>%
  column_spec(2, width = "5%") %>%
  column_spec(3, width = "25%") %>%
  column_spec(4, width = "8%") %>%
  column_spec(5, width = "54%") %>%
  row_spec(which(complete_table$Decision == "INCLUDE"), bold = TRUE, background = "#d4edda")
```

# Cochrane Library and Google Scholar

## Cochrane Library (CENTRAL)

The extended search strategy was also tested on Cochrane Library using the following search equation:

**Search conducted on:** `r format(Sys.time(), '%Y-%m-%d')`

**Search equation:**

```
#1 ("sexual dysfunction" OR "sexual function" OR "sexual health" OR "sexuality"
    OR "erectile dysfunction" OR "libido" OR "dyspareunia"):ti,ab,kw

#2 ("neuromuscular disease" OR "neuromuscular disorder" OR "muscular dystrophy"
    OR "myotonic dystrophy" OR "Steinert" OR "amyotrophic lateral sclerosis"
    OR "motor neuron disease" OR "spinal muscular atrophy" OR "Kennedy disease"
    OR "myasthenia gravis" OR "Lambert-Eaton" OR "Charcot-Marie-Tooth"
    OR "dermatomyositis" OR "polymyositis" OR "inclusion body myositis"
    OR "myopathy" OR "polyneuropathy" OR "Guillain-Barre" OR "Guillain-Barré"
    OR "transthyretin amyloidosis" OR "familial amyloid polyneuropathy"
    OR "Duchenne" OR "Becker muscular dystrophy" OR "facioscapulohumeral"
    OR "limb-girdle" OR "Emery-Dreifuss" OR "Pompe disease"
    OR "periodic paralysis"):ti,ab,kw

#3 NOT ("diabetes" OR "diabetic" OR "fibromyalgia" OR "neurofibromatosis"
    OR "multiple sclerosis" OR "cancer" OR "stroke" OR "epilepsy"
    OR "spinal cord injury" OR "animal model" OR "mice" OR "mouse"):ti,ab,kw

#4 #1 AND #2 AND #3
```

**Publication date limit:** 1983-2024

**Result:** No additional relevant articles were identified beyond those already captured by PubMed search and citation tracking.

## Google Scholar

Due to Google Scholar's limitations with complex Boolean queries (maximum query length, no MeSH support), the search was conducted using multiple shorter targeted queries:

**Search queries executed:**

| Query | Search string | Results reviewed |
|-------|--------------|------------------|
| 1 | `"sexual dysfunction" OR "sexuality" "spinal muscular atrophy"` | First 100 |
| 2 | `"sexual dysfunction" OR "sexuality" "myotonic dystrophy" OR "Steinert disease"` | First 100 |
| 3 | `"sexual function" "Duchenne muscular dystrophy"` | First 100 |
| 4 | `"sexuality" OR "sexual health" "amyotrophic lateral sclerosis"` | First 100 |
| 5 | `"sexual dysfunction" "myasthenia gravis"` | First 100 |
| 6 | `"sexuality" "Charcot-Marie-Tooth"` | First 100 |
| 7 | `"sexual function" "dermatomyositis" OR "polymyositis"` | First 100 |
| 8 | `"erectile dysfunction" "transthyretin amyloidosis" OR "familial amyloid polyneuropathy"` | First 100 |
| 9 | `"sexual dysfunction" "Kennedy disease" OR "spinal and bulbar muscular atrophy"` | First 100 |
| 10 | `"sexuality" "facioscapulohumeral muscular dystrophy"` | First 100 |

**Exclusion filters applied:** Results were filtered to exclude articles on diabetes, multiple sclerosis, spinal cord injury, animal studies, and pediatric populations.

**Result:** No additional relevant articles were identified beyond those already captured by PubMed search and citation tracking. All relevant articles found in Google Scholar were already included in the PubMed search results or had been identified through citation tracking.

# Conclusion

## Summary

The extended search strategy using disease-specific terms identified **16 additional records** not captured by the original "neuromuscular disease/disorder" umbrella terms.

After title/abstract and full-text screening:

- **1 article met inclusion criteria** and was added to the review:
  - Hausmanowa-Petrusewicz I et al. (1983). *X-linked adult form of spinal muscular atrophy.* Journal of Neurology.
  - This article reports original data on sexual dysfunction (erectile dysfunction, reduced libido) and reproductive abnormalities (reduced fertility, testicular atrophy) in Kennedy disease (SBMA).

- **15 articles were excluded** for the following reasons:
  - Population not meeting inclusion criteria (caregivers, not patients): 1
  - Congenital/developmental abnormalities, not sexual dysfunction: 2
  - No specific data on sexual dysfunction reported: 7
  - Language not meeting criteria (Russian): 1
  - Not a primary neuromuscular disease: 1
  - Focus on other outcomes (treatment, survival, infection): 3

## Impact on Review

The sensitivity analysis resulted in:

- **Total included studies: 27** (26 original + 1 additional)
- The additional study provides data on **Kennedy disease (SBMA)**, a condition not previously covered in the review
- This confirms the comprehensiveness of the original search strategy combined with citation tracking

# Reproducibility

All analyses were conducted using R version `r R.version.string`.

The complete code and data are available in this repository:

- `scripts/`: R scripts for PubMed search and analysis
- `results/`: Output CSV files with all screened articles
- `data/`: Original search equations

## Session Info

```{r session-info}
sessionInfo()
```

---

*This sensitivity analysis is provided as supplementary material for transparency and reproducibility.*
