---
title: "Search Strategy Sensitivity Analysis"
subtitle: "Sexual Health in Neuromuscular Diseases - Scoping Review"
author: "Audrey El Kaïm"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(dplyr)
library(knitr)
library(kableExtra)
```

# Context

## Background

This scoping review aimed to map and synthesize evidence on sexual dysfunction in adults with neuromuscular diseases (NMDs). The original search strategy used umbrella terms ("neuromuscular disease", "neuromuscular disorder") combined with sexual health terms.

As PubMed MeSH does not include a single unified heading for all NMDs—distributing them across many disease-level MeSH terms—a sensitivity analysis was conducted to verify the comprehensiveness of the search strategy.

## Objective

To verify the comprehensiveness of the search strategy by:

1. Expanding the search with disease-specific and category terms
2. Comparing results with the original search
3. Identifying any additional relevant articles not captured by umbrella terms
4. Documenting all screening decisions for transparency

---

# Original Search Strategies

## PubMed - Original Search Equation

The original search strategy used umbrella terms combined with sexual health terms:

```
("sexual behaviour"[MeSH Terms] OR ("sexual"[All Fields] AND "behaviour"[All Fields])
 OR "sexual behaviour"[All Fields] OR "sexual"[All Fields] OR "sexually"[All Fields]
 OR "sexualities"[All Fields] OR "sexuality"[MeSH Terms] OR "sexuality"[All Fields]
 OR "sexualization"[All Fields] OR "sexualize"[All Fields] OR "sexualized"[All Fields]
 OR "sexualizing"[All Fields] OR "sexuals"[All Fields])

AND

("neuromuscular diseases"[MeSH Terms] OR ("neuromuscular"[All Fields] AND "diseases"[All Fields])
 OR "neuromuscular diseases"[All Fields] OR ("neuromuscular"[All Fields] AND "disorders"[All Fields])
 OR "neuromuscular disorders"[All Fields])

NOT (neurofibromatosis[MeSH Terms])
NOT (diabetes[MeSH Terms])
NOT (fibromyalgia[MeSH Terms])
NOT (chronic fatigue syndrome[MeSH Terms])
NOT (mice OR mouse)
```

**Period:** 1983-2024

## Google Scholar - Original Search Equation

```
sexuality neuromuscular disorders sexual OR life
-dimorphic -"cerebral palsy" -prostatitis -cancer -stroke
-"chronic respiratory failure" -"multiple sclerosis" -epilepsy
-abuse -diabetes -cardiac -fibromyalgia -neurofibromatosis
-"spinal cord injury" -mouse -"cauda equina lesions"
```

## Cochrane Library - Original Search Equation

```
("sexual dysfunction" OR "sexual function" OR "sexual health" OR "sexuality"
 OR "libido" OR "erectile dysfunction" OR "dyspareunia" OR "orgasmic disorder"
 OR "hypoactive sexual desire disorder" OR "sexual satisfaction")

AND

("neuromuscular disease" OR "neuromuscular disorder")

NOT

("diabetes" OR "fibromyalgia" OR "neurofibromatosis" OR "multiple sclerosis"
 OR "cancer" OR "stroke" OR "epilepsy" OR "spinal cord injury"
 OR "mouse" OR "animal model")
```

---

# Extended Search Strategy

## Rationale

Since PubMed MeSH does not include a single unified heading for all neuromuscular diseases, articles indexed only under disease-specific terms (e.g., "Duchenne muscular dystrophy", "amyotrophic lateral sclerosis") might not be captured by umbrella "neuromuscular" terms.

## Disease-Specific Terms Added

The search strategy was expanded to include specific disease names in 9 groups:

### Group 1: Umbrella + General Myopathies
```
"neuromuscular diseases"[MeSH Terms] OR "neuromuscular disease"[Title/Abstract]
OR "neuromuscular disorder"[Title/Abstract] OR "myopathy"[Title/Abstract]
OR "myopathies"[Title/Abstract] OR "muscular dystrophy"[Title/Abstract]
OR "muscular dystrophies"[Title/Abstract] OR "Muscular Dystrophies"[MeSH Terms]
OR "congenital myopathy"[Title/Abstract] OR "congenital myopathies"[Title/Abstract]
OR "metabolic myopathy"[Title/Abstract] OR "mitochondrial myopathy"[Title/Abstract]
OR "Mitochondrial Myopathies"[MeSH Terms]
```

### Group 2: Inflammatory Myopathies
```
"myositis"[MeSH Terms] OR "inflammatory myopathy"[Title/Abstract]
OR "inflammatory myopathies"[Title/Abstract] OR "dermatomyositis"[Title/Abstract]
OR "Dermatomyositis"[MeSH Terms] OR "polymyositis"[Title/Abstract]
OR "Polymyositis"[MeSH Terms] OR "inclusion body myositis"[Title/Abstract]
OR "Myositis, Inclusion Body"[MeSH Terms] OR "necrotizing myopathy"[Title/Abstract]
OR "immune-mediated necrotizing myopathy"[Title/Abstract]
OR "antisynthetase syndrome"[Title/Abstract]
```

### Group 3: Motor Neuron Diseases
```
"motor neuron disease"[Title/Abstract] OR "motor neurone disease"[Title/Abstract]
OR "Motor Neuron Disease"[MeSH Terms] OR "amyotrophic lateral sclerosis"[Title/Abstract]
OR "Amyotrophic Lateral Sclerosis"[MeSH Terms] OR "spinal muscular atrophy"[Title/Abstract]
OR "Muscular Atrophy, Spinal"[MeSH Terms] OR "spinal and bulbar muscular atrophy"[Title/Abstract]
OR "Bulbo-Spinal Atrophy, X-Linked"[MeSH Terms] OR "Kennedy disease"[Title/Abstract]
OR "primary lateral sclerosis"[Title/Abstract]
```

### Group 4: Peripheral Neuropathies
```
"peripheral neuropathy"[Title/Abstract] OR "peripheral neuropathies"[Title/Abstract]
OR "polyneuropathy"[Title/Abstract] OR "polyneuropathies"[Title/Abstract]
OR "Polyneuropathies"[MeSH Terms] OR "hereditary motor and sensory neuropathy"[Title/Abstract]
OR "Charcot-Marie-Tooth disease"[Title/Abstract] OR "Charcot-Marie-Tooth Disease"[MeSH Terms]
OR "hereditary neuropathy with liability to pressure palsies"[Title/Abstract]
OR "chronic inflammatory demyelinating polyneuropathy"[Title/Abstract]
OR "chronic inflammatory demyelinating polyradiculoneuropathy"[Title/Abstract]
OR "Polyradiculoneuropathy, Chronic Inflammatory Demyelinating"[MeSH Terms]
OR "Guillain-Barre syndrome"[Title/Abstract] OR "Guillain-Barre Syndrome"[MeSH Terms]
OR "multifocal motor neuropathy"[Title/Abstract]
```

### Group 5: Amyloid Neuropathies
```
"transthyretin amyloidosis"[Title/Abstract] OR "ATTR amyloidosis"[Title/Abstract]
OR "hereditary transthyretin amyloidosis"[Title/Abstract]
OR "Amyloid Neuropathies, Familial"[MeSH Terms]
OR "familial amyloid polyneuropathy"[Title/Abstract]
OR "amyloid neuropathy"[Title/Abstract]
```

### Group 6: Neuromuscular Junction Disorders
```
"neuromuscular junction disease"[Title/Abstract]
OR "Neuromuscular Junction Diseases"[MeSH Terms]
OR "myasthenia gravis"[Title/Abstract] OR "Myasthenia Gravis"[MeSH Terms]
OR "Lambert-Eaton myasthenic syndrome"[Title/Abstract]
OR "Lambert-Eaton Myasthenic Syndrome"[MeSH Terms]
OR "congenital myasthenic syndrome"[Title/Abstract]
OR "congenital myasthenic syndromes"[Title/Abstract]
OR "Myasthenic Syndromes, Congenital"[MeSH Terms]
```

### Group 7: Myotonic Dystrophy and Channelopathies
```
"myotonic dystrophy"[Title/Abstract] OR "Myotonic Dystrophy"[MeSH Terms]
OR "Steinert disease"[Title/Abstract] OR "myotonia congenita"[Title/Abstract]
OR "Myotonia Congenita"[MeSH Terms] OR "paramyotonia congenita"[Title/Abstract]
OR "periodic paralysis"[Title/Abstract] OR "hyperkalemic periodic paralysis"[Title/Abstract]
OR "hypokalemic periodic paralysis"[Title/Abstract]
OR "muscle channelopathy"[Title/Abstract] OR "muscular channelopathy"[Title/Abstract]
```

### Group 8: Specific Muscular Dystrophies
```
"Duchenne muscular dystrophy"[Title/Abstract] OR "Muscular Dystrophy, Duchenne"[MeSH Terms]
OR "Becker muscular dystrophy"[Title/Abstract]
OR "facioscapulohumeral muscular dystrophy"[Title/Abstract]
OR "Muscular Dystrophy, Facioscapulohumeral"[MeSH Terms]
OR "limb-girdle muscular dystrophy"[Title/Abstract]
OR "limb girdle muscular dystrophy"[Title/Abstract]
OR "Muscular Dystrophies, Limb-Girdle"[MeSH Terms]
OR "Emery-Dreifuss muscular dystrophy"[Title/Abstract]
OR "Muscular Dystrophy, Emery-Dreifuss"[MeSH Terms]
OR "oculopharyngeal muscular dystrophy"[Title/Abstract]
OR "distal muscular dystrophy"[Title/Abstract] OR "distal myopathy"[Title/Abstract]
OR "congenital muscular dystrophy"[Title/Abstract]
```

### Group 9: Metabolic Myopathies
```
"Pompe disease"[Title/Abstract] OR "Glycogen Storage Disease Type II"[MeSH Terms]
OR "acid maltase deficiency"[Title/Abstract] OR "McArdle disease"[Title/Abstract]
OR "Glycogen Storage Disease Type V"[MeSH Terms]
OR "glycogen storage disease myopathy"[Title/Abstract]
```

## Important Methodological Note: Ambiguous Acronyms

**Ambiguous acronyms were deliberately avoided** to prevent false positives:

| Acronym | Intended meaning | Common false positive |
|---------|-----------------|----------------------|
| SMA | Spinal Muscular Atrophy | Smooth Muscle Actin (histology) |
| ALS | Amyotrophic Lateral Sclerosis | Acid-labile subunit, Advanced life support |
| BMD | Becker Muscular Dystrophy | Bone Mineral Density |
| MG | Myasthenia Gravis | Magnesium |
| FAP | Familial Amyloid Polyneuropathy | Familial Adenomatous Polyposis |
| IBM | Inclusion Body Myositis | Company name |
| DMD | Duchenne Muscular Dystrophy | Various |
| FSHD | Facioscapulohumeral Dystrophy | Not widely used |
| LGMD | Limb-Girdle Muscular Dystrophy | Not widely used |

**Only full disease names were used** in the extended search to ensure specificity.

---

# Extended Search - Cochrane Library

## Search Equation

**Database:** Cochrane Library (CENTRAL)
**Search date:** February 2026
**Publication date limit:** 1983-2024

```
#1 Sexual health terms (Title, Abstract, Keywords):
("sexual dysfunction" OR "sexual function" OR "sexual health" OR "sexuality"
 OR "erectile dysfunction" OR "libido" OR "dyspareunia" OR "orgasmic disorder"
 OR "hypoactive sexual desire" OR "sexual satisfaction" OR "impotence"):ti,ab,kw

#2 Neuromuscular disease terms (Title, Abstract, Keywords):
("neuromuscular disease" OR "neuromuscular disorder" OR "muscular dystrophy"
 OR "myotonic dystrophy" OR "Steinert disease" OR "amyotrophic lateral sclerosis"
 OR "motor neuron disease" OR "motor neurone disease"
 OR "spinal muscular atrophy" OR "Kennedy disease" OR "spinal and bulbar muscular atrophy"
 OR "myasthenia gravis" OR "Lambert-Eaton"
 OR "Charcot-Marie-Tooth" OR "hereditary motor sensory neuropathy"
 OR "dermatomyositis" OR "polymyositis" OR "inclusion body myositis"
 OR "inflammatory myopathy"
 OR "myopathy" OR "polyneuropathy" OR "peripheral neuropathy"
 OR "Guillain-Barre" OR "Guillain-Barré" OR "chronic inflammatory demyelinating"
 OR "transthyretin amyloidosis" OR "familial amyloid polyneuropathy" OR "ATTR amyloidosis"
 OR "Duchenne" OR "Becker muscular dystrophy"
 OR "facioscapulohumeral" OR "limb-girdle" OR "Emery-Dreifuss"
 OR "Pompe disease" OR "McArdle disease"
 OR "periodic paralysis" OR "myotonia congenita"):ti,ab,kw

#3 Exclusions:
NOT ("diabetes" OR "diabetic neuropathy" OR "fibromyalgia" OR "neurofibromatosis"
 OR "multiple sclerosis" OR "cancer" OR "stroke" OR "epilepsy"
 OR "spinal cord injury" OR "animal model" OR "mice" OR "mouse" OR "rat"):ti,ab,kw

#4 Final search: #1 AND #2 AND #3
```

**Result:** No additional relevant articles identified beyond PubMed search and citation tracking.

---

# Extended Search - Google Scholar

## Search Strategy

Due to Google Scholar's limitations (maximum query length ~256 characters, no MeSH support, no structured Boolean), the search was conducted using **10 targeted queries**, each combining a sexual health term with a specific NMD:

| # | Search Query | Results Screened |
|---|-------------|------------------|
| 1 | `"sexual dysfunction" OR "sexuality" "spinal muscular atrophy"` | First 100 results |
| 2 | `"sexual dysfunction" OR "sexuality" "myotonic dystrophy" OR "Steinert disease"` | First 100 results |
| 3 | `"sexual function" OR "sexuality" "Duchenne muscular dystrophy"` | First 100 results |
| 4 | `"sexuality" OR "sexual health" "amyotrophic lateral sclerosis"` | First 100 results |
| 5 | `"sexual dysfunction" OR "erectile dysfunction" "myasthenia gravis"` | First 100 results |
| 6 | `"sexuality" OR "sexual function" "Charcot-Marie-Tooth"` | First 100 results |
| 7 | `"sexual function" OR "sexuality" "dermatomyositis" OR "polymyositis"` | First 100 results |
| 8 | `"erectile dysfunction" "transthyretin amyloidosis" OR "familial amyloid polyneuropathy"` | First 100 results |
| 9 | `"sexual dysfunction" "Kennedy disease" OR "spinal and bulbar muscular atrophy"` | First 100 results |
| 10 | `"sexuality" OR "sexual function" "facioscapulohumeral muscular dystrophy"` | First 100 results |

**Exclusion filters applied manually:** Articles on diabetes, multiple sclerosis, spinal cord injury, animal studies, and pediatric populations were excluded during screening.

**Result:** No additional relevant articles identified beyond PubMed search and citation tracking.

---

# Results

## Search Comparison Summary

```{r load-data}
# Load results
original <- read.csv("results/pubmed_original_search.csv", stringsAsFactors = FALSE)
new_raw <- read.csv("results/pubmed_new_articles_raw.csv", stringsAsFactors = FALSE)
high_relevance <- read.csv("results/pubmed_new_high_relevance.csv", stringsAsFactors = FALSE)
final_table <- read.csv("results/FINAL_EXCLUSION_TABLE_EN.csv", stringsAsFactors = FALSE)
```

```{r summary-table}
summary_df <- data.frame(
  Step = c(
    "Original search (umbrella terms only)",
    "Extended search (disease-specific terms)",
    "New records identified",
    "High relevance (NMD term in title)",
    "After duplicate removal with included studies",
    "Meeting inclusion criteria"
  ),
  N = c(
    nrow(original),
    nrow(original) + nrow(new_raw),
    nrow(new_raw),
    nrow(high_relevance),
    nrow(final_table),
    sum(final_table$Decision == "INCLUDE")
  )
)

kable(summary_df, col.names = c("Screening Step", "N"), align = c("l", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(6, bold = TRUE, background = "#d4edda")
```

---

## Complete Screening Table: 16 Additional Articles

The following table presents **all 16 articles** identified through the extended search strategy that were not captured by the original umbrella terms.

Each article was screened at full-text level. Decisions and detailed justifications are provided.

```{r complete-screening-table}
# Create table with PubMed links
screening_table <- final_table %>%
  mutate(
    PMID_Link = paste0('<a href="https://pubmed.ncbi.nlm.nih.gov/', PMID, '/" target="_blank">', PMID, '</a>'),
    Short_Title = ifelse(nchar(Title) > 80, paste0(substr(Title, 1, 77), "..."), Title)
  ) %>%
  select(PMID_Link, Year, Short_Title, Decision, Justification)

kable(screening_table,
      col.names = c("PMID", "Year", "Title", "Decision", "Justification"),
      escape = FALSE,
      align = c("c", "c", "l", "c", "l")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = TRUE,
                font_size = 11) %>%
  column_spec(1, width = "7%") %>%
  column_spec(2, width = "5%") %>%
  column_spec(3, width = "25%") %>%
  column_spec(4, width = "8%", bold = TRUE) %>%
  column_spec(5, width = "55%") %>%
  row_spec(which(final_table$Decision == "INCLUDE"), bold = TRUE, background = "#d4edda") %>%
  row_spec(which(final_table$Decision == "EXCLUDE"), background = "#f8f9fa")
```

---

## Article Included in Review

```{r included-article, results='asis'}
included <- final_table %>% filter(Decision == "INCLUDE")

if (nrow(included) > 0) {
  cat("### ", included$Title[1], "\n\n")
  cat("- **PMID:** [", included$PMID[1], "](https://pubmed.ncbi.nlm.nih.gov/", included$PMID[1], "/)\n", sep = "")
  cat("- **Year:** ", included$Year[1], "\n")
  cat("- **Decision:** INCLUDED\n\n")
  cat("**Justification:**\n\n")
  cat(included$Justification[1], "\n")
}
```

---

## Articles Excluded from Review (n = `r sum(final_table$Decision == "EXCLUDE")`)

### Summary of Exclusion Reasons

```{r exclusion-summary}
excluded <- final_table %>% filter(Decision == "EXCLUDE")

# Categorize exclusion reasons
exclusion_categories <- data.frame(
  Reason = c(
    "Population not meeting criteria (caregivers, not patients)",
    "Congenital/developmental abnormalities, not sexual dysfunction",
    "No specific data on sexual dysfunction reported",
    "Language not meeting criteria (Russian)",
    "Not a primary neuromuscular disease",
    "Focus on other outcomes (treatment, survival, infection)"
  ),
  N = c(1, 2, 7, 1, 1, 3)
)

kable(exclusion_categories, col.names = c("Exclusion Reason", "N"), align = c("l", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

### Detailed Exclusion Table

```{r excluded-details}
excluded_table <- excluded %>%
  mutate(
    PMID_Link = paste0('<a href="https://pubmed.ncbi.nlm.nih.gov/', PMID, '/" target="_blank">', PMID, '</a>')
  ) %>%
  select(PMID_Link, Year, Title, Justification)

kable(excluded_table,
      col.names = c("PMID", "Year", "Title", "Reason for Exclusion"),
      escape = FALSE,
      align = c("c", "c", "l", "l")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE,
                font_size = 11) %>%
  column_spec(1, width = "8%") %>%
  column_spec(2, width = "5%") %>%
  column_spec(3, width = "30%") %>%
  column_spec(4, width = "57%")
```

---

# Conclusion

## Summary of Findings

The extended search strategy using disease-specific terms identified **`r nrow(new_raw)` additional records** not captured by the original "neuromuscular disease/disorder" umbrella terms.

After filtering for high relevance (NMD term in title) and removing duplicates with already-included studies, **16 articles** underwent full-text screening.

**Final result:**

- **1 article met inclusion criteria** and was added to the review
- **15 articles were excluded** for various reasons (see table above)

## Article Added to Review

**Hausmanowa-Petrusewicz I, Borkowska J, Janczewski Z. (1983)**
*X-linked adult form of spinal muscular atrophy.*
Journal of Neurology. [PMID: 6191009](https://pubmed.ncbi.nlm.nih.gov/6191009/)

This article reports original data on **Kennedy disease (SBMA)**, including:

- Sexual dysfunction: erectile dysfunction, reduced libido
- Reproductive abnormalities: reduced fertility, testicular atrophy, impaired spermatogenesis

## Impact on Review

- **Total included studies:** 27 (26 original + 1 additional)
- The additional study provides data on **Kennedy disease (SBMA)**, a condition not previously covered in the original review
- This confirms the comprehensiveness of the original search strategy combined with citation tracking

## Verification of Search Strategy Comprehensiveness

The sensitivity analysis demonstrates that:

1. The original umbrella terms ("neuromuscular disease/disorder") captured the vast majority of relevant literature
2. Disease-specific terms identified only **1 additional relevant article** out of 301 new records
3. Extended searches in **Cochrane Library** and **Google Scholar** yielded no additional relevant articles
4. The search strategy, combined with citation tracking, is comprehensive

---

# Reproducibility

## Data and Code Availability

All analyses were conducted using R version `r R.version.string`.

The complete code and data are available in this repository:

| Folder | Contents |
|--------|----------|
| `scripts/` | R scripts for PubMed search and analysis |
| `results/` | Output CSV files with all screened articles |
| `data/` | Original search equations |

## Key Files

| File | Description |
|------|-------------|
| `scripts/search_comparison_pubmed.R` | Main PubMed search comparison script |
| `scripts/filter_relevant_nmd.R` | Relevance filtering script |
| `scripts/extract_new_articles_final.R` | Metadata extraction script |
| `scripts/create_exclusion_table.R` | Final exclusion table generation |
| `results/FINAL_EXCLUSION_TABLE_EN.csv` | Complete screening results |
| `results/pubmed_original_search.csv` | Original search results |
| `results/pubmed_new_articles_raw.csv` | New articles from extended search |

## Session Info

```{r session-info}
sessionInfo()
```

---

*This sensitivity analysis was conducted in February 2026 and is provided as supplementary material for transparency and reproducibility.*
